The pollination trade-off

### 2018-12-01 paper/manuscript.Rmd
Typos in draft info

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters; approx. `r format(round(msc_wordcount$n_words_stri/10)*10-90, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.

@@

* Now using AICc instead of AIC to evaluate models (no change in results)
* Traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances. Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
* The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
* Introduced visit efficacy instead of the share in the pollen pool as a predictor in the model. Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models. 
* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper teratment to the facilitation/competition question.

## To do

@@

* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
* I got feedback that "denote" in \lr{denote} might be overly formal? 
* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you preffer to keep data private?

>>>>

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx. `r format(round(msc_wordcount$n_words_stri/10)*10-340, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.

@@

* Now using AICc instead of AIC to evaluate models (no change in results)
* Traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances. Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
* The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
* Introduced visit efficacy instead of the share in the pollen pool as a predictor in the model. Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models. 
* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper treatment to the facilitation/competition question.

## Todo

@@

* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
* I got feedback that "denote" in \lr{denote} might be overly formal? 
* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
